---
title: "STATS 250 Lab 7 Report"
author: "YOUR NAME GOES HERE IN QUOTES"
date: "TODAY'S DATE GOES HERE IN QUOTES"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    theme: lumen
    css: assets/styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!("checkmate" %in% installed.packages()))
  install.packages('checkmate')
source("plot_norm.R") # This imports the shuffle_two_groups() function
set.seed(51021) # Note setting the seed!!
```

# Instructions

Welcome to Lab 7! Complete the following exercises designed to help you understand the simulation process for making inference about a population proportion. It is important that you keep your answers inside the ".answer" blocks. Do NOT delete the three colon blocks (:::) and keep your responses between them. Use the tutorial for help, and feel free to ask questions on Piazza or email your lab instructor.

Depending on your instruction method (synchronous or asynchronous), complete the following exercises collaboratively.

1. **Synchronous remote:** Work with your peers in breakout rooms during the synchronous lab.
1. **Asynchronous remote:** Use Piazza for asynchronous collaboration.

**Collaborators:** If applicable, replace this text with the names of anyone you collaborated with on this project.

**NOTE:** If you perform a calculation in R and assign it a name but do not print the value in your knitted document, we reserve the right to deduct points.

# Background

:::{.background}
A popular uprising that started on January 25, 2011 in Egypt led to the 2011 Egyptian Revolution. Polls show that about 69% of American adults followed the news about the political crisis and demonstrations in Egypt closely during the first couple weeks following the start of the uprising. Among a random sample of 35 high school students, it was found that only 20 of them followed the news about Egypt closely during this time.^[https://news.gallup.com/poll/146003/americans-views-egypt-sharply-negative.aspx]
:::

# Lab Assignment

## Question 1
:::{.question}
Write the hypotheses for testing whether the proportion of high school students who closely followed the news about Egypt is different from the 69% reported value for American adults. Use words and symbols.
:::

:::{.answer}

- $H_0:$ *replace this text with your null hypothesis*
- $H_A:$ *replace this text with your alternative hypothesis*

:::

## Question 2
:::{.question}
Let's set up a simulation to test our hypotheses. Create a vector called `bagOfChips` that consists of appropriate numbers of `"blue"` and `"yellow"` chips. `bagOfChips` should contain 100 elements in total.
:::

:::{.answer}
```{r question2, error = T}
# Replace this comment with code required for Question 2. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 3
:::{.question}
Use the `sample()` and `replicate()` functions to run the simulation 1000 times. Make sure to save your results by assigning them a name. Revisit Lab 5 if you need a refresher on the code!
:::

:::{.answer}
```{r question3, error = T}
# Replace this comment with code required for Question 3. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 4
:::{.question}
Plot your simulation results in a histogram, and draw vertical line(s) to help visualize the p-value.
:::

:::{.answer}
```{r question4, error = T}
# Replace this comment with code required for Question 4. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 5
:::{.question}
Using your simulation results, compute the p-value for the hypotheses you wrote in Question 1. Make sure your answer shows up in your knitted document.
:::

:::{.answer}
```{r question5, error = T}
# Replace this comment with code required for Question 5. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 6
:::{.question}
Assuming that the null hypothesis is true, we can say that the simulated $\hat{p}$ values will approximately follow a N(0.69, 0.0782) distribution.

Using this distribution, find the probability of observing a value of $\hat{p}$ between 0.5 and 0.75. Include an appropriate visualization using `plot_norm()`.
:::

:::{.answer}
```{r question6, error = T}
# Replace this comment with code required for Question 6. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 7
:::{.question}
Assuming that the null hypothesis is true, we can say that the simulated $\hat{p}$ values will approximately follow a N(0.69, 0.0782) distribution.

Find the 95% quantile of this distribution (i.e., the number such that 95% of the distribution is to the left). Include an appropriate visualization using `plot_norm()`.
:::

:::{.answer}
```{r question7, error = T}
# Replace this comment with code required for Question 7. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 8
:::{.question}
Assuming that the null hypothesis is true, we can say that the simulated $\hat{p}$ values will approximately follow a N(0.69, 0.0782) distribution.

Use this distribution to approximate the p-value for your hypothesis test. Include an appropriate visualization using `plot_norm()`.
:::

:::{.answer}
```{r question8, error = T}
# Replace this comment with code required for Question 8. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

# Wrap-Up and Submission

At the top of the document, make sure you've changed the `author` field to your name (in quotes!). If you'd like, change the date as well.

When you've finished the lab, click the **Knit** button one last time.

## Submission instructions

### If you're using RStudio Cloud

1.  In the Files pane, check the box next to `lab07-report.html`.
2.  Click More \> Export...
3.  Click Download and save the file on your computer in a folder you'll remember and be able to find later. You can just call the file `lab07-report.html` or whatever else you'd like (as long as you remember what you called it).

### If you're using RStudio installed on your computer

1.  locate the `lab07-report.html` file on your computer. The file will be saved in the location indicated at the top of the files pane.

### Submission to Canvas

1.  Click the "Assignments" panel on the left side of the page. Scroll to find "Lab 7", and open the assignment. Click "Submit Assignment".
2.  Towards the bottom of the page, you'll be able to choose `lab07-report.html` from the folder you saved it in from RStudio Cloud or noted if you're using RStudio Desktop. **You will only be able to upload a .html file -- do not upload any other file type.**
3.  Click "Submit Assignment". You're done!
